Numerical trajectory patterns of floating macroalgae

### 2021-02-21 thesis_chapter_3.Rmd
more detail added to table and figure captions

```{r map, echo=FALSE, message=FALSE, warning=FALSE, strip.white=TRUE, fig.cap="Figure 1:Map of the study domain. This is a temporary map until issues with the map script are resolved."}

@@

```{r sim table, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Details for each simulation run for the study"}

@@

```{r morphology table, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE, fig.cap="Table summarising the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation."}

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure 3: Comparison of density of particles within each grid cell for the end run time of each scenario. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation.', fig.height=10.2, fig.width=7.5}

@@

```{r distance plot, message=FALSE, warning=FALSE, echo = FALSE, fig.cap="Figure 4: Boxplots of total distance of all particles from the release site over the course of the simulation for each exposure scenario."}
dis_plot
```

@@

```{r shape data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 5: Comparison of trajectory data between a kelp sphere and kelp cylinder. Plot A is the comparison of mean trajectories, plot B is the comparison of distance travelled by all particles, and plot C and D are the density plots for simulations using a sphere and cylinderical shape coefficient.", fig.height=8, fig.width=8}

>>>>

```{r map, echo=FALSE, message=FALSE, warning=FALSE, strip.white=TRUE, fig.cap="Figure 1:Map of the study domain and the main features pertaining to transport in the region. In panel A, the map of the entire South African coastline and the main currents presented. The resulting eddies and filaments from the Agulhas retroflection and study area are presented. In panel B, the splitting of the Benguela Jet, eddie features and general flow of the study domain are presented."}

@@

```{r sim table, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Details for each simulation run for the study. The table cosists of parameterisations for each scenario. The ID coloumn refers to the syntax used in the relevant OceanParcels script. Type refers to either a passive particle with no drag behaviour or a kelp particle that has been advected with any drag exposure. The drag exposure column refers to the parameterisations regarding the level of water and wind drag simulated."}

@@

```{r morphology table, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE, fig.cap="Table summarising the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation. Approximate shape refers to the dimensions of the geometric shape used to represent a particular morpholgical characteristic. Equations used are the equations relating to the dimensions used for the geometric shape estimate. Plant dimensions are the measurements used, collected in previous work by @coppin2020, used to calculate the associated surface areas. The total surface areas for each plant characteristic for each surface area type make up the remaining columns."}

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure 3: Comparison of density plots at the end run time of each scenario. The plots are regular hexagons within the density of particles is calculated. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation. The mean trajectories for each scenario are also plotted for comparison.', fig.height=10.2, fig.width=7.5}

@@

```{r distance plot, message=FALSE, warning=FALSE, echo = FALSE, fig.cap="Figure 4: Boxplots of total distance travelled by all particles from the release site over the course of the simulation for each scenario. The x-axis represents the scenario number and the y-axis is the distance travelled in kilometers. The lower and upper "hinges" correspond to the first and third quartiles. The whiskers represent the range, solid black lines represent the median and black dots are outliers."}
dis_plot
```

@@

```{r shape data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 5: Comparison of trajectory data between a kelp sphere and kelp cylinder. Plot A is the comparison of mean trajectories, plot B is the comparison of total distance travelled by all particles, and plot C and D are the density plots for simulations using a sphere and cylinderical shape coefficient.", fig.height=8, fig.width=8}
